### 2023-03-01 related.tex
Update related work; minor edits to various sections in type hole inference (Raef)

\section{Related Work}
\label{sec:related}

Jeremy Siek Gradual Typing with Inference
- Siek's type inference halts when it can't solve, ours doesn't

>>>>

\section{Related Work}
\label{sec:related}
\textbf{Type Inference and Unification} In \emph{Gradual Typing with Unification Based Inference}, a version of unification for gradually typed languages based on Huet's unification algorithm is explored ~\cite{GradualInfer} ~\cite{Huet}. Other common approaches to unification are generally based on Hinley-Milner type inference ~\cite{MilnerInfer}. These algorithms are efficient, but can fail to solve constraints in the face of inconsistencies.

\textbf{Correcting Sets and Assigning Blame} The generation of correcting sets is a common approach to error localization. The correcting set is assigned blame for failure in type inference \cite{sherrloc} \cite{typeinferDif} \cite{Pavlinovic2015}. Other approaches to assigning blame include statistically derived approaches that leverage machine learning to predict the best candidates for blame \cite{SeidelBlame}.

\textbf{Dynamic Witnesses} Explanations for type errors can arguably be best illustrated by providing inputs that elicit runtime errors. This procedure can be used to generate graphs for visualizing the execution of witnesses and heuristically identify the source of errors with 70\% accuracy \cite{Seidel2016}.
